---
title: "team.Rmd"
author: "Zihao Han; Xi Wang"
date: "February 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1 overall number of chocolate bars that was rated
##### the total number of cholate bars is **1852**
##### and the rating is range from **1 to 5**

```{r}
choco<- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")

length(choco$Rating)
range(choco$Rating)

```

## Q2 number of ratings depend on the year

```{r}

hist(choco$Review.Date)

```

##Q3 ratings compare across different company locations
##### The top 6 company locations are USA, France, Canada, UK, Italy, Ecuador

```{r}
table <- table(choco$Company.Location)

table <- sort.int(table(choco$Company.Location),decreasing = T)

barplot(head(table))

```

##Q4 Brainstorm
###Question: what is the relationship between rating and cocoa persentage.

##Q5 Answer 
##### the rating of chocolate bars is significant affected by the percentage of cocos, with p-value=0.000 R^2^=0.026. 

```{r}

model1 <- lm (choco$Rating ~ choco$Cocoa.Pct)
summary (model1)

```
